Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-09-30 response-reviewers-2.tex

\vspace{0.5cm}

% ********** comienzo del texto  *******************

{\bf Response to reviewers' comments}

We are very grateful to the reviewers for their kind comments. We have rewritten
the paper quite extensively, incorporating requested changes, but also
attempting to give another angle that makes this paper apart from what was
already published in this other one

Merelo, J.J. et al. (2022). Exploring the Role of Chatbots and Messaging
Applications in Higher Education: A Teacher's Perspective. In: Zaphiris, P.,
Ioannou, A. (eds) Learning and Collaboration Technologies. Novel Technological
Environments. HCII 2022. Lecture Notes in Computer Science, vol 13329. Springer,
Cham. https://doi.org/10.1007/978-3-031-05675-8\_16

@@

% https://www.scribbr.com/apa-style/apa-seventh-edition-changes/

% -> answer 10      
{\it 10.     Is the article written in a clear and intelligible style to a reasonably well-informed international professional readership? Yes. However, there are a few grammatical errors. I suggest the authors proofread the manuscript to correct them.}

The authors apologise for the grammatical errors and have strived to fix them and to avoid them in the new paragraphs.

% -> answer 11
{\it 11.     Other few comments the authors should consider:
   a.   Reorganize the conclusion section to highlight the main aim of the research work briefly, key findings and the significance of the work, and future research work.
   b.   Some of the paragraphs in the conclusion section can be moved to Discussion. The Discussion section can be captioned as Discussion and Implications to cater for some of the paragraphs that will be moved to this section. For example, paragraphs on Page 23, Line 16, "In our survey..." and Page 23, Line 37, "One of the questions we made in the second survey..." should be moved to the Discussion and Implication section.}

To address these final comments:
    a. as cited before, the abstrac and other sections have been rewritten
    highlighting the key findings and the significance of this work as compared
    with the others.

### 2022-09-30 response-reviewers-2.tex

The authors want to thank the reviewer for evaluating positively those aspect of the paper.

% -> answer 9

9.      Does the article clearly reference citations and quotations using the APA 7th edition? Partly, some of the references do not follow APA 7th edition. For example, the following references don't follow APA 7th edition referencing style
     a.   O'Boyle, 2014. O'Boyle, N. (2014). Front row friendships: Relational dialectics and identity negotiations by mature students at univerty. Communication Education, 63(3):169-191
     b. Panah and Babar, 2020. Panah, E. and Babar, M. Y. (2020). A survey of WhatsApp as a tool for instructor-learner dialogue, learner-content dialogue, and learner-learner dialogue. International Journal of Educational and Pedagogical
 Sciences, 14(12):1198 - 1205.
     c. Perez et al., 2020. Perez, J. Q., Daradoumis, T., and Puig, J. M. M. (2020). Rediscovering the use of chatbots in education: A systematic literature review. Computer Applications in Engineering Education, 28(6):1549- 1565.
     d. Ranoliya et al., 2017. Ranoliya, B. R., Raghuwanshi, N., and Singh, S. (2017). Chatbot for university related faqs. In 2017 International Conference on Advances in Computing, Communications and Informatics (ICACCI), pages 1525-1530. IEEE.
     e. Roblyer et al., 2010. Roblyer, M., McDaniel, M., Webb, M., Herman, J., and Witty, J. V. (2010). Findings on facebook in higher education: A comparison of college faculty and student uses and perceptions of social networking sites. The Internet and Higher Education, 13(3):134 - 140.

{\it We have used, as instructed by the template, the {\tt apalike} style in our
  LaTeX source, as well as used standard BiBTeX files downloaded from the
  publication itself. No tweaking has been mede on these, so I don't see what we
  can do about it, other than report a bug in the style to the authors.

We have been checking out the issue, and apparently the problem is that the 7th
edition is not well covered by the current LaTeX styles, which are stuck at the
6th edition. A pretty extensive change in tooling is needed, unfortunately,
including the style of bibliography citation and the tool used for doing
that. So while there's a path for doing this, we do not think it is something we
should devote our time in the current version of the paper, if the reviewer does
not mind. We will certainly do so as required by publication when (or if) this
paper is finally accepted}

### 2022-09-30 response-reviewers-2.tex

% -> answer 10      
{\it 10.     Is the article written in a clear and intelligible style to a reasonably well-informed international professional readership? Yes. However, there are a few grammatical errors. I suggest the authors proofread the manuscript to correct them.}

The authors apologise for the grammatical errors and have strived to fix them and to avoid them in the new paragraphs.

% -> answer 11
{\it 11.     Other few comments the authors should consider:
   a.   Reorganize the conclusion section to highlight the main aim of the research work briefly, key findings and the significance of the work, and future research work.
   b.   Some of the paragraphs in the conclusion section can be moved to Discussion. The Discussion section can be captioned as Discussion and Implications to cater for some of the paragraphs that will be moved to this section. For example, paragraphs on Page 23, Line 16, "In our survey..." and Page 23, Line 37, "One of the questions we made in the second survey..." should be moved to the Discussion and Implication section.}

To address these final comments:
    a. as cited before, the abstract and other sections have been rewritten
    highlighting the key findings and the significance of this work as compared
    with the others.

    b. We have changed the title and moved the indicated paragraph. Thanks for
    the suggestion.

### 2022-09-30 edubots_surveys.Rnw
Addressing last question

\textcolor{black}{A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%). From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%). In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%). In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).}

@@

% ********************** Discussion section *******************
\section{Discussion}

@@

@@

% Only some COVID-response relationship.
In our survey, we could not find an answer about the right moment introducing chatbot technologies. Response to questions related to change of
behaviour during and after the first, stay at home, stage of the pandemic do not suggest that major (or minor)
crisis could be an opportunity to introduce new technologies, since it does not
bring major changes in attitude. A minor crisis would be, for instance, rollout
of a new higher education law\footnote{We seem to have one of these, at least in
  Spain, every 10 years or so.}, or introduction of new degrees. Although
external changes do offer the chance of piloting new technologies, they do not
seem to bring changes in attitudes in the teaching staff (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, "official" support is one of
the factors that is most valued by teachers).

>>>>

A total of 205 teachers responded to the second survey: 187 graduate teachers (91.2\%) and 18 student teachers (8.8\%). From those, 124 were male (60.5\%), 65 female (31.7\%) and 16 teachers preferred not to indicate their gender (7.8\%). In terms of age, the majority of the participants (n=70) was again, as in the first survey, 45-55 years old (34.1\%), while 67 teachers were 35-45 years old (32.7\%), 42 were 25-35 (20.5\%) and 26 teachers were older than 55 (12.7\%). In terms of teaching experience, 59 teachers had a teaching experience of 16-25 years (28.8\%), 51 teachers had 6-15 years (24.9\%) and 0-5 years of experience (24.9\%), and 44 teachers more than 25 years of teaching experience (21.5\%).

@@

% ********************** Discussion section *******************
\section{Discussion and implications}

@@

% Only some COVID-response relationship.
In our survey, we could not find an answer about the right moment for introducing chatbot technologies. Response to questions related to change of
behaviour during and after the first stay at home, stage of the pandemic do not suggest that a major (or minor)
crisis could be an opportunity to introduce new technologies, since it does not
bring major changes in attitude (as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in
  Spain, every 10 years or so.}), or simply introduction of new degrees. Although
changes driven by external forces do offer the chance of piloting new technologies, they do not
seem to bring internal changes in attitudes in the teaching staff (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, "official" support is one of
the factors that is most valued by teachers).

@@
